Influence of Connectivity on Dung Beetle Communities

### 2025-05-02 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
added extra methods bit.

All dung beetles were counted and identified to species as described in @nemes_illustrated_2015-1 and @edmonds_taxonomic_2023. Fifteen individuals of each species with adequate captures was dried to equalibrium and weighed for biomass measurements.

>>>>

All dung beetles were counted and identified to species as described in @nemes_illustrated_2015-1 and @edmonds_taxonomic_2023. Fifteen individuals of each species with adequate captures were dried to equalibrium and weighed for biomass measurements. Voucher specimcens for each species will be deposited at the Florida State Collection of Arthropods.
